\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2021-11-23 main.Rmd
add more content

**point to common feature: spatial level variables + time level variables relates to Table 13 in Tidy data paper**  
Usually, this type of spatio-temporal data don't come in as a single table. Tidy data principle (...) prescribes each type of observational unit to form a table. This would suggest two tables to store the data, one for spatial-level and  one for temporal-level. The Table 13 in the tidy data paper present a structure like this and the author argues the lack of tools to work with relational data. \newline

**My proposal**  
Recent software development in R has proposed several relational data structure: `tidygraph`[@tidygraph] for graph manipulation, `dm` [@dm] for relational data model, while spatio-temporal data could benefit from having its own relational data structure. In this paper, we propose a tidy data structure for vector spaio-temporal data.  \newline

@@

# Existing data structure for spatio and temporal data

@@

  1) A data structure that handles spatial and temporal dimension in a relational structure. This derives from the 3rd tidy data principal.
  2) An intuitive and easy to use interface that fits into the tidyverse ecosystem, and
  3) Compatibility with the latest spatial and temporal data structure. This would give users the flexibility to use work from existing packages.

\newpage
# Workflow/ Data pipeline

Now we introduce cubble in a data pipeline structure (review the concept of data pipeline? at least articulate its importance - automation, predictable of output)

@@

**Format of st in the wild**  
Analysing this type of data requires less considerations on the geographical geometry type and map projection but more on how measures in these fixed locations changes across the time domain and whether these changes are related for adjacent locations. For example, when nearby areas show patterns that are regular enough, visualising spatio-temporal data can 1) discover regional time series features, i.e. trend and seasonality, 2) find the Waldo sites from the crowd, and 3) see how correlation of nearby sites changes across time. \newline

## Cubble

**We form a cubble by defining abc... - Nested and long form**  
When manipulating the spatial dimension it uses a nest form that:

@@

When manipulating the temporal dimension, it uses the long form that:

  - each combination of group and timestamp occupies a row
  - time-related variables are displayed, and
  - group-related variables are not explicitly displayed but can be accessed through the `meta` attribute.

### stretch

*By default build a nested cubble, stretch to long, create spatial attributes*

### tamp

*Tamp to nested, use the spatial attributes*

### Support on hierarchical structure

## Tidyverse compatibility

*list supported tidyverse functions*

## Others

@@

Spatio-temporal data don't usually come to the analysts as a whole piece. A way to look at these data is to divide it into spatial and temporal dimension with an ID that links between the two. The first row in Figure \ref{fig:cubble-diagram} illustrates this representation where in the spatial dimension, the data is characterised by `id`, `lat`, `long`. $V_s$ in the last column represents all the other site-wise variables, for example, elevation and full name etc. The temporal dimension, on the other hand, can be characterised by `id` and `t` with $V_t$ representing all the time-wise variables. In climate data, this could include precipitation, maximum or minimum temperature, and wind speed etc.

```{r cubble-diagram, echo = FALSE, fig.cap="Cubble diagram", out.height="40%", fig.align='center'}
knitr::include_graphics(here::here("figures/input-formats/input-formats.001.png"))
```

@@

A cubble, in essence, wires both dimensions in the spatio-temporal data into one object while provide two forms for manipulation the spatial and temporal dimension separately.

When manipulating the spatial dimension it uses a nest form that:

When manipulating the temporal dimension, it uses the long form that:

  - each combination of group and timestamp occupies a row
  - time-related variables are displayed, and
  - group-related variables are not explicitly displayed but can be accessed through the `meta` attribute.

>>>>

**point to common feature: spatial level variables + time level variables relates to Table 13 in Tidy data paper**  
Usually, this type of spatio-temporal data does not necessarily come in as a single table. Tidy data principle [@tidydata] prescribes each type of observational unit to form a table. This would suggest two tables to store the data, one for spatial-level and one for temporal-level. The Table 13 in @tidydata presents a structure like this and the author argues the lack of tools to work with relational data like such. \newline

**My proposal**  
Recent software development in R has proposed several relational data structure: `tidygraph`[@tidygraph] for graph manipulation, `dm` [@dm] for relational data model, while spatio-temporal data could benefit from having its own relational data structure that identifies the essential spati0-temporal element: site identifier, time identifier, geographic coordinates. In this paper, we propose a tidy data structure for vector spaio-temporal data.  \newline

@@

# Existing data structure for spatio and temporal data {#lit-review}

@@

  1) A data structure that handles spatial and temporal dimension in a relational structure. This derives from the 3rd tidy data principal.
  2) An intuitive and easy to use interface that fits into the tidyverse ecosystem, and
  3) Compatibility with the latest spatial and temporal data structure. This would give users the flexibility to use the work in existing packages.

\newpage
# Cubble data structure

@@

Spatio-temporal data don't usually come to the analysts in various forms. Figure \ref{fig:cubble-diagram} groups them into four categories. Despite whichever form the data is in, all the forms have a group identifier, `key`, a time column, `t`, and variables that either various across group, i.e. `lon`, `lat`, $C_s$, or across time, i.e. $V_t$. These identifiers will be the building blocks for the data structure introduced below.

```{r cubble-diagram, echo = FALSE, fig.cap="Illustration of incoming data formats for spatio-temporal data. (1) Data comes in as a single table; (2) Separate tables for spatial and temporal variables; (3) A single table with all the parameters used to query the database and a separate table for queried data; and (4) Cubical data in array or NetCDF format.", fig.align='center', out.height = "15%"}
knitr::include_graphics(here::here("figures/input-formats/input-formats.001.png"))
```

## A new data structure: cubble

A cubble, in essence, wires the spatial and temporal dimension into a single object while provides two forms for manipulation each dimension separately.

In the nest form, Figure \ref{fig:def-cubble}a), a cubble:

@@

In the long form, Figure \ref{fig:def-cubble}b), a cubble:

  - defines the combination of group and timestamp as a row
  - displays time-related variables, along with the group identifier in columns, and
  - stores group-related variables as a attributes called `spatial`.

```{r def-cubble, echo = FALSE, fig.align="center", out.height="30%", fig.cap = "Illustration of nested and long cubble."}
knitr::include_graphics(here::here("figures/def-cubble/def-cubble.001.png"))
```

\newpage
## Create a cubble in the nested form

To create a cubble, you can use `as_cubble` with proper supply of `key`, `index`, and `coords`. [`key` defines whether a variable is spatial or temperal by looking at whether it varies across `key`. For example, `lat` is a spatial variable since for one `id` there's only one `lat` value. `index` and `coords` prescribes the temporal index and spaital coordinates used in the data. These are common variables that should present in the point pattern spatio-temporal data.] The cubble created by default is in the nested form.  \newline

```{r}
(cubble_nested <- climate_flat %>% 
  as_cubble(key = id, index = date, coords = c("long", "lat")))
```

In the `cubble` header, you can read the key variable + number, bbox, and also the name of variable nested in the `ts` column. Here in this example, the temporal variables are precipitation, `prcp`, maximum temporature, `tmax`, and minimum temperature, `tmin`.

In this structure, the nested form is suitable for manipulating the spatial dimension of the data and this would include manipulating variables that 1) are inherently spatial and 2) summarise the temporal variables by `key`. Under the hood, the nested cubble is built on top of the rowwise dataframe (`rowwise_df`). This is design to simplify the code when working with the temporal variables - they are nested into the list-column `ts`.

## Stretch a nested cubble into the long form

The verb `stretch()` switch the cubble from the nested form into a long form. Under the hood, it first extracts the spatial variables into a separate tibble to store in the attribute `spatial` and then unnests the `ts` column to show the temporal content:

```{r}
(cubble_long <- cubble_nested %>% stretch(ts))
```

Notice here that the third line in the header is changed to reflect the spatial variables stored. This is a format suitable for computing time-wise variables.

## Tamp a long cubble back to the nested form

Manipulation on the spatial and temporal dimension can be an iterative process. Many times, we may decide to go back to the nested form after some temporal manipulation. The verb to switch a long cubble back to the nested form is `tamp()`:

```{r}
(cubble_back <- cubble_long %>% tamp())
```

## Migrate spatial variables to a long cubble

As an output to be supplied to further visualisation or modelling, analysts would usually like the spatial and temporal variables to be in the same table. `migrate()` moves the spatial variables in the attribute `spatial` into the long form cubble.

```{r}
(cubble_long %>% migrate(long, lat))
```

## Support on hierarchical structure

`switch_key()`

## Integrating into a tidy workflow

Building from an underlying `tbl_df` structure, it is natural to implement methods available in `dplyr` to `cubble`. Supported methods in the `cubble` with `dplyr` generics includes: `mutate`, `filter`, `summarise`, `select`, `arrange`, `rename`, `left_join`, `group_by`, `ungroup`, and the slice family (`slice_head`, `slice_tail`, `slice_sample`, `slice_min` and `slice_max`) \textcolor{red}{into a table}.

`cubble` is also compatible with `tsibble` in the sense that the original list-column can be a `tbl_ts` object. Duplicates and gaps shoudl be first checked before structuring the data into a cubble. If the input data is a `tsibble` object, the long form cubble is also a `tsibble` where users can directly apply time series operations.

@@

@@

### 2021-11-23 main.tex
add more content

\textbf{point to common feature: spatial level variables + time level
variables relates to Table 13 in Tidy data paper}\\
Usually, this type of spatio-temporal data don't come in as a single
table. Tidy data principle (\ldots) prescribes each type of
observational unit to form a table. This would suggest two tables to
store the data, one for spatial-level and one for temporal-level. The
Table 13 in the tidy data paper present a structure like this and the
author argues the lack of tools to work with relational data. \newline

\textbf{My proposal}\\
Recent software development in R has proposed several relational data
structure: \texttt{tidygraph}\citep{tidygraph} for graph manipulation,
\texttt{dm} \citep{dm} for relational data model, while spatio-temporal
data could benefit from having its own relational data structure. In
this paper, we propose a tidy data structure for vector spaio-temporal
data. \newline

@@

\hypertarget{existing-data-structure-for-spatio-and-temporal-data}{%
\section{Existing data structure for spatio and temporal
data}\label{existing-data-structure-for-spatio-and-temporal-data}}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  A data structure that handles spatial and temporal dimension in a
  relational structure. This derives from the 3rd tidy data principal.
\item
  An intuitive and easy to use interface that fits into the tidyverse
  ecosystem, and
\item
  Compatibility with the latest spatial and temporal data structure.
  This would give users the flexibility to use work from existing
  packages.
\end{enumerate}

@@

Now we introduce cubble in a data pipeline structure (review the concept
of data pipeline? at least articulate its importance - automation,
predictable of output)

@@

\textbf{Format of st in the wild}\\
Analysing this type of data requires less considerations on the
geographical geometry type and map projection but more on how measures
in these fixed locations changes across the time domain and whether
these changes are related for adjacent locations. For example, when
nearby areas show patterns that are regular enough, visualising
spatio-temporal data can 1) discover regional time series features,
i.e.~trend and seasonality, 2) find the Waldo sites from the crowd, and
3) see how correlation of nearby sites changes across time. \newline

\hypertarget{cubble}{%
\subsection{Cubble}\label{cubble}}

\textbf{We form a cubble by defining abc\ldots{} - Nested and long
form}\\
When manipulating the spatial dimension it uses a nest form that:

@@

When manipulating the temporal dimension, it uses the long form that:

\begin{itemize}
\tightlist
\item
  each combination of group and timestamp occupies a row
\item
  time-related variables are displayed, and
\item
  group-related variables are not explicitly displayed but can be
  accessed through the \texttt{meta} attribute.
\end{itemize}

\hypertarget{stretch}{%
\subsubsection{stretch}\label{stretch}}

\emph{By default build a nested cubble, stretch to long, create spatial
attributes}

\hypertarget{tamp}{%
\subsubsection{tamp}\label{tamp}}

\emph{Tamp to nested, use the spatial attributes}

\hypertarget{support-on-hierarchical-structure}{%
\subsubsection{Support on hierarchical
structure}\label{support-on-hierarchical-structure}}

\hypertarget{tidyverse-compatibility}{%
\subsection{Tidyverse compatibility}\label{tidyverse-compatibility}}

\emph{list supported tidyverse functions}

\hypertarget{others}{%
\subsection{Others}\label{others}}

@@

Spatio-temporal data don't usually come to the analysts as a whole
piece. A way to look at these data is to divide it into spatial and
temporal dimension with an ID that links between the two. The first row
in Figure \ref{fig:cubble-diagram} illustrates this representation where
in the spatial dimension, the data is characterised by \texttt{id},
\texttt{lat}, \texttt{long}. \(V_s\) in the last column represents all
the other site-wise variables, for example, elevation and full name etc.
The temporal dimension, on the other hand, can be characterised by
\texttt{id} and \texttt{t} with \(V_t\) representing all the time-wise
variables. In climate data, this could include precipitation, maximum or
minimum temperature, and wind speed etc.

{\centering \includegraphics[width=1\linewidth,height=0.4\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/input-formats/input-formats.001}

\caption[Cubble diagram]{Cubble diagram}\label{fig:cubble-diagram}
\end{figure}
\end{CodeChunk}

@@

A cubble, in essence, wires both dimensions in the spatio-temporal data
into one object while provide two forms for manipulation the spatial and
temporal dimension separately.

When manipulating the spatial dimension it uses a nest form that:

When manipulating the temporal dimension, it uses the long form that:

\begin{itemize}
\tightlist
\item
  each combination of group and timestamp occupies a row
\item
  time-related variables are displayed, and
\item
  group-related variables are not explicitly displayed but can be
  accessed through the \texttt{meta} attribute.
\end{itemize}

>>>>

\textbf{point to common feature: spatial level variables + time level
variables relates to Table 13 in Tidy data paper}\\
Usually, this type of spatio-temporal data does not necessarily come in
as a single table. Tidy data principle \citep{tidydata} prescribes each
type of observational unit to form a table. This would suggest two
tables to store the data, one for spatial-level and one for
temporal-level. The Table 13 in \citet{tidydata} presents a structure
like this and the author argues the lack of tools to work with
relational data like such. \newline

\textbf{My proposal}\\
Recent software development in R has proposed several relational data
structure: \texttt{tidygraph}\citep{tidygraph} for graph manipulation,
\texttt{dm} \citep{dm} for relational data model, while spatio-temporal
data could benefit from having its own relational data structure that
identifies the essential spati0-temporal element: site identifier, time
identifier, geographic coordinates. In this paper, we propose a tidy
data structure for vector spaio-temporal data. \newline

@@

\hypertarget{lit-review}{%
\section{Existing data structure for spatio and temporal
data}\label{lit-review}}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  A data structure that handles spatial and temporal dimension in a
  relational structure. This derives from the 3rd tidy data principal.
\item
  An intuitive and easy to use interface that fits into the tidyverse
  ecosystem, and
\item
  Compatibility with the latest spatial and temporal data structure.
  This would give users the flexibility to use the work in existing
  packages.
\end{enumerate}

@@

@@

Spatio-temporal data don't usually come to the analysts in various
forms. Figure \ref{fig:cubble-diagram} groups them into four categories.
Despite whichever form the data is in, all the forms have a group
identifier, \texttt{key}, a time column, \texttt{t}, and variables that
either various across group, i.e.~\texttt{lon}, \texttt{lat}, \(C_s\),
or across time, i.e.~\(V_t\). These identifiers will be the building
blocks for the data structure introduced below.

{\centering \includegraphics[width=1\linewidth,height=0.15\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/input-formats/input-formats.001}

\caption[Illustration of incoming data formats for spatio-temporal data]{Illustration of incoming data formats for spatio-temporal data. (1) Data comes in as a single table; (2) Separate tables for spatial and temporal variables; (3) A single table with all the parameters used to query the database and a separate table for queried data; and (4) Cubical data in array or NetCDF format.}\label{fig:cubble-diagram}
\end{figure}
\end{CodeChunk}

\hypertarget{a-new-data-structure-cubble}{%
\subsection{A new data structure:
cubble}\label{a-new-data-structure-cubble}}

A cubble, in essence, wires the spatial and temporal dimension into a
single object while provides two forms for manipulation each dimension
separately.

In the nest form, Figure \ref{fig:def-cubble}a), a cubble:

@@

In the long form, Figure \ref{fig:def-cubble}b), a cubble:

\begin{itemize}
\tightlist
\item
  defines the combination of group and timestamp as a row
\item
  displays time-related variables, along with the group identifier in
  columns, and
\item
  stores group-related variables as a attributes called
  \texttt{spatial}.
\end{itemize}

{\centering \includegraphics[width=1\linewidth,height=0.3\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/def-cubble/def-cubble.001}

\caption[Illustration of nested and long cubble]{Illustration of nested and long cubble.}\label{fig:def-cubble}
\end{figure}
\end{CodeChunk}

\hypertarget{create-a-cubble-in-the-nested-form}{%
\subsection{Create a cubble in the nested
form}\label{create-a-cubble-in-the-nested-form}}

To create a cubble, you can use \texttt{as\_cubble} with proper supply
of \texttt{key}, \texttt{index}, and \texttt{coords}. {[}\texttt{key}
defines whether a variable is spatial or temperal by looking at whether
it varies across \texttt{key}. For example, \texttt{lat} is a spatial
variable since for one \texttt{id} there's only one \texttt{lat} value.
\texttt{index} and \texttt{coords} prescribes the temporal index and
spaital coordinates used in the data. These are common variables that
should present in the point pattern spatio-temporal data.{]} The cubble
created by default is in the nested form. \newline

\begin{CodeChunk}
\begin{CodeInput}
R> (cubble_nested <- climate_flat %>% 
+   as_cubble(key = id, index = date, coords = c("long", "lat")))
\end{CodeInput}
\begin{CodeOutput}
# cubble:   id [5]: nested form
# bbox:     [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# temporal: date [date], prcp [dbl], tmax [dbl], tmin [dbl]
  id            lat  long  elev name           wmo_id ts                
  <chr>       <dbl> <dbl> <dbl> <chr>           <dbl> <list>            
1 ASN00009021 -31.9  116.  15.4 perth airport   94610 <tibble [366 x 4]>
2 ASN00010311 -31.9  117. 179   york            94623 <tibble [366 x 4]>
3 ASN00010614 -32.9  117. 338   narrogin        94627 <tibble [366 x 4]>
4 ASN00014015 -12.4  131.  30.4 darwin airport  94120 <tibble [366 x 4]>
5 ASN00015131 -17.6  134. 220   elliott         94236 <tibble [366 x 4]>
\end{CodeOutput}
\end{CodeChunk}

In the \texttt{cubble} header, you can read the key variable + number,
bbox, and also the name of variable nested in the \texttt{ts} column.
Here in this example, the temporal variables are precipitation,
\texttt{prcp}, maximum temporature, \texttt{tmax}, and minimum
temperature, \texttt{tmin}.

In this structure, the nested form is suitable for manipulating the
spatial dimension of the data and this would include manipulating
variables that 1) are inherently spatial and 2) summarise the temporal
variables by \texttt{key}. Under the hood, the nested cubble is built on
top of the rowwise dataframe (\texttt{rowwise\_df}). This is design to
simplify the code when working with the temporal variables - they are
nested into the list-column \texttt{ts}.

\hypertarget{stretch-a-nested-cubble-into-the-long-form}{%
\subsection{Stretch a nested cubble into the long
form}\label{stretch-a-nested-cubble-into-the-long-form}}

The verb \texttt{stretch()} switch the cubble from the nested form into
a long form. Under the hood, it first extracts the spatial variables
into a separate tibble to store in the attribute \texttt{spatial} and
then unnests the \texttt{ts} column to show the temporal content:

\begin{CodeChunk}
\begin{CodeInput}
R> (cubble_long <- cubble_nested %>% stretch(ts))
\end{CodeInput}
\begin{CodeOutput}
# cubble:  date, id [5]: long form
# bbox:    [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# spatial: lat [dbl], long [dbl], elev [dbl], name [chr], wmo_id [dbl]
   id          date        prcp  tmax  tmin
   <chr>       <date>     <dbl> <dbl> <dbl>
 1 ASN00009021 2020-01-01     0  31.9  15.3
 2 ASN00009021 2020-01-02     0  24.9  16.4
 3 ASN00009021 2020-01-03     6  23.2  13  
 4 ASN00009021 2020-01-04     0  28.4  12.4
 5 ASN00009021 2020-01-05     0  35.3  11.6
 6 ASN00009021 2020-01-06     0  34.8  13.1
 7 ASN00009021 2020-01-07     0  32.8  15.1
 8 ASN00009021 2020-01-08     0  30.4  17.4
 9 ASN00009021 2020-01-09     0  28.7  17.3
10 ASN00009021 2020-01-10     0  32.6  15.8
# ... with 1,820 more rows
\end{CodeOutput}
\end{CodeChunk}

Notice here that the third line in the header is changed to reflect the
spatial variables stored. This is a format suitable for computing
time-wise variables.

\hypertarget{tamp-a-long-cubble-back-to-the-nested-form}{%
\subsection{Tamp a long cubble back to the nested
form}\label{tamp-a-long-cubble-back-to-the-nested-form}}

Manipulation on the spatial and temporal dimension can be an iterative
process. Many times, we may decide to go back to the nested form after
some temporal manipulation. The verb to switch a long cubble back to the
nested form is \texttt{tamp()}:

\begin{CodeChunk}
\begin{CodeInput}
R> (cubble_back <- cubble_long %>% tamp())
\end{CodeInput}
\begin{CodeOutput}
# cubble:   id [5]: nested form
# bbox:     [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# temporal: date [date], prcp [dbl], tmax [dbl], tmin [dbl]
  id            lat  long  elev name           wmo_id ts                
  <chr>       <dbl> <dbl> <dbl> <chr>           <dbl> <list>            
1 ASN00009021 -31.9  116.  15.4 perth airport   94610 <tibble [366 x 4]>
2 ASN00010311 -31.9  117. 179   york            94623 <tibble [366 x 4]>
3 ASN00010614 -32.9  117. 338   narrogin        94627 <tibble [366 x 4]>
4 ASN00014015 -12.4  131.  30.4 darwin airport  94120 <tibble [366 x 4]>
5 ASN00015131 -17.6  134. 220   elliott         94236 <tibble [366 x 4]>
\end{CodeOutput}
\end{CodeChunk}

\hypertarget{migrate-spatial-variables-to-a-long-cubble}{%
\subsection{Migrate spatial variables to a long
cubble}\label{migrate-spatial-variables-to-a-long-cubble}}

As an output to be supplied to further visualisation or modelling,
analysts would usually like the spatial and temporal variables to be in
the same table. \texttt{migrate()} moves the spatial variables in the
attribute \texttt{spatial} into the long form cubble.

\begin{CodeChunk}
\begin{CodeInput}
R> (cubble_long %>% migrate(long, lat))
\end{CodeInput}
\begin{CodeOutput}
# cubble:  date, id [5]: long form
# bbox:    [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# spatial: lat [dbl], long [dbl], elev [dbl], name [chr], wmo_id [dbl]
   id          date        prcp  tmax  tmin  long   lat
   <chr>       <date>     <dbl> <dbl> <dbl> <dbl> <dbl>
 1 ASN00009021 2020-01-01     0  31.9  15.3  116. -31.9
 2 ASN00009021 2020-01-02     0  24.9  16.4  116. -31.9
 3 ASN00009021 2020-01-03     6  23.2  13    116. -31.9
 4 ASN00009021 2020-01-04     0  28.4  12.4  116. -31.9
 5 ASN00009021 2020-01-05     0  35.3  11.6  116. -31.9
 6 ASN00009021 2020-01-06     0  34.8  13.1  116. -31.9
 7 ASN00009021 2020-01-07     0  32.8  15.1  116. -31.9
 8 ASN00009021 2020-01-08     0  30.4  17.4  116. -31.9
 9 ASN00009021 2020-01-09     0  28.7  17.3  116. -31.9
10 ASN00009021 2020-01-10     0  32.6  15.8  116. -31.9
# ... with 1,820 more rows
\end{CodeOutput}
\end{CodeChunk}

\hypertarget{support-on-hierarchical-structure}{%
\subsection{Support on hierarchical
structure}\label{support-on-hierarchical-structure}}

\texttt{switch\_key()}

\hypertarget{compatibility-with-existing-software}{%
\subsection{Compatibility with existing
software}\label{compatibility-with-existing-software}}

Building from an underlying \texttt{tbl\_df} structure, it is natural to
implement methods available in \texttt{dplyr} to \texttt{cubble}.
Supported methods in the \texttt{cubble} with \texttt{dplyr} generics
includes: \texttt{mutate}, \texttt{filter}, \texttt{summarise},
\texttt{select}, \texttt{arrange}, \texttt{rename}, \texttt{left\_join},
\texttt{group\_by}, \texttt{ungroup}, and the slice family
(\texttt{slice\_head}, \texttt{slice\_tail}, \texttt{slice\_sample},
\texttt{slice\_min} and \texttt{slice\_max})
\textcolor{red}{into a table}.

\texttt{cubble} is also compatible with \texttt{tsibble} in the sense
that the original list-column can be a \texttt{tbl\_ts} object.
Duplicates and gaps shoudl be first checked before structuring the data
into a cubble. If the input data is a \texttt{tsibble} object, the long
form cubble is also a \texttt{tsibble} where users can directly apply
time series operations.

@@

@@
